Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-17 awipev-CO2.Rmd
added package hms added install.packages

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(plotly)
library(htmlwidgets)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

@@

* Serveur : awipev-co2 (193.50.85.104)
* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
* Pour se connecter à awipev-co2.obs-vlfr.fr
    + ssh awipev@awipev-co2.obs-vlfr.fr
* Intervention sur le serveur :
    + ssh awipev@awipev-co2.obs-vlfr.fr
    + rebooting Ubuntu server: sudo shutdown -r now
    + to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    + To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    + To restart shiny server: sudo systemctl restart shiny-server
        - update shiny server: follow procedure detailed on the shiny web page Data processing
* To install R packages:
    + ssh gattuso@awipev-co2.obs-vlfr.fr
    + sudo R (then password)
    + install.packages (tidyverse")

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
# if (!require("plotly")) install.packages("plotly")
# library(plotly)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
knitr::opts_chunk$set(echo = TRUE)

@@

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
d_all <
```

@@

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

@@

* Serveur : awipev-co2 (193.50.85.104)
* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
* Pour se connecter à awipev-co2.obs-vlfr.fr
    + ssh awipev@awipev-co2.obs-vlfr.fr
* Intervention sur le serveur :
    + ssh awipev@awipev-co2.obs-vlfr.fr
    + rebooting Ubuntu server: sudo shutdown -r now
    + to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    + To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    + To restart shiny server: sudo systemctl restart shiny-server
        - update shiny server: follow procedure detailed on the shiny web page Data processing
* To install R packages:
    + ssh gattuso@awipev-co2.obs-vlfr.fr
    + sudo R (then password)
    + install.packages("tidyverse")
